---
title: "project 1"
output:
  pdf_document: default
  html_document: default
date: "2023-09-28"
---
In China, the differential treatment of sons and daughters has long been a very serious and very real part of gender discrimination. When I ran R-shiny, I found that sons appeared more often in happy moments than daughters. I think this partly reflects people's gender discrimination towards their children. So I revealed file bag_of_words.csv, and sorted the data to see if there was a difference between the frequency of sons and the frequency of daughters in male and female happy moments.Here's my code below.

```{r}
library(dplyr)
library(tidyverse)
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(gridExtra)
library(ngram)
library(ggplot2)


head(bag_of_words)

bag_of_words <- read.csv("/Users/roy/Documents/GitHub/ads-fall2023-project1-RoyWZH99/data/bag_of_words.csv")
temp <- bag_of_words %>% 
  count(!!as.name("gender"), word) %>%
  group_by(!!as.name("gender")) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(!!as.name("gender"), proportion)

temp
```




```{r}
library(reshape2)

df <- temp %>% filter(word =="son"|word == "daughter" |word == "children")
df1 <- melt(df)
df1

ggplot(df1,aes(x=factor(word,levels = unique(word)), y=ifelse(variable== "f", value,-value),fill=variable))+
  geom_bar(stat = "identity")+
  coord_flip()+
  geom_text(                                                  
    aes(label=sprintf("%.5f", value),                                          
        hjust = ifelse(variable == "Up", -0.4, 1.1)           
        ),size=2)+
  scale_y_continuous(                                      
    labels = abs,                                            
    expand = expansion(mult = c(0.1, 0.1)))  +
  scale_fill_manual(values = c("f" = "lightcoral", "m" = "lightblue"),labels = c("f" = "female", "m" = "male")) +
  labs(x = "Word", y = "Proportion")
   
```
We can find that for both men and women, son appear more frequently in happy moments than daughter. This reflects the fact that despite efforts to eliminate gender inequality, gender discrimination still exists in child-rearing.
